\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Parallel Algorithms Coursework}
\author{Fraser Waters and Michael Thorpe}
%\date{}                                           % Activate to display a given date or no date

\begin{document}
\maketitle

\section{Failure detectors}

Failure detectors maintain a collection of suspected processes. A suspected
process is one that is suspected of being in a crashed state at the time the
failure detector is evaluated.

Detectors in different processes do not have to agree and detectors do not have
to be correct, that is a detector may suspect a correct process or not suspect
a crashed process.

Detectors can be classified by their completeness and accuracy. A complete
detector will suspect crashed processes.  An accurate detector will not detect
correct processes. A trivial complete detector is a detector that suspects
every process. A trivial accurate detector is one that suspect no processes.
Clearly neither of these are very useful or interesting, and a trade-off
between accuracy and completeness is more useful.

A detector is strongly complete if every crashed process is eventually
suspected by every correct process. A detector is strongly accurate if no
correct process is ever suspected, it is weakly accurate if there is at least
one correct process that is never suspected. A detector is eventually strongly
accurate if it eventually no longer suspects any correct process, a detector is
eventually weakly accurate if eventually there is a correct process that is not
suspected. 

\section{Implementations}

\subsection{Perfect failure detector}

The implementation of the perfect failure detector assumes that no message is
delayed for more than two times the average delay. As long as we wait for at
least $\text{time between heartbeats} + 2 * delay$ we will never incorrectly
suspect a process. 

If we subsequently receive a heartbeat from a process which we suspect, we remove
it from the suspects list.

\subsection{Eventually perfect failure detector}

The eventually perfect failure detector keeps track of the maximum delay
between heartbeats from each process. If a process heartbeat is not received
within two times the maximum delay tracked so far it is suspected.

\subsection{Leadership Election}

We simply choose the process with the highest PID that is not suspect as the leader.
For this we need to assume perfect communication between all processes if we want
all (correct) processes to elect the same leader.

\subsection{Consensus}



\section{Relationships between classes}

\begin{description}
	\item[$P$ (perfect)] Strongly complete and strongly accurate
	\item[$S$ (strong)] Strongly complete and weakly accurate
	\item[$\diamond P$ (eventually perfect)] Strongly complete and eventually strongly accurate
	\item[$\diamond S$ (eventually strong)] Strongly complete and eventually weakly accurate
\end{description}

$P$ emulates $S$. 
$\diamond P$ emulates $\diamond S$, as it is eventually strongly accurate which
is more specific then $\diamond S$ that is only eventually weakly accurate.
$S$ emulates $\diamond S$ as is is weakly accurate immediately, this is equivalent to $\diamond S$ eventually time being 0.
$S$ can not emulate $\diamond P$ as $\diamond P$ is strongly accurate, which is more specific than $S$.
$\diamond S$ can not emulate any of the others, it is the weakest failure detector.

\begin{tabular}{|l|c|c|c|c|c|c|}
\hline
Row emulates column  & $P$ & $\diamond P$ & $S$ & $\diamond S$ \\ \hline
$P$                  & N/A & Yes          & Yes & Yes          \\ \hline
$\diamond P$         & No  & N/A          & No  & Yes          \\ \hline
$S$                  & No  & No           & N/A & Yes          \\ \hline
$\diamond S$         & No  & Yes          & No  & N/A          \\ \hline
\end{tabular}


\section{Weak completeness}

A system that satisfies weak completeness can be augmented to emulate strong
completeness by sharing knowledge. That is, once a process $A$ suspects a
process $B$ then $A$ will broadcast a message that it suspects $B$. All the
processes receiving this message will now add $B$ to their suspected list as
well. This spread of knowledge will eventually result in all processes
suspecting all faulty processes.

\end{document}  
